manuscript

### 2023-05-15 manuscript.rmd
added Manocci reference

Drifter tracks were rounded to nearest 20 minutes, lost buoys (1,2,3,5,6,9,11) and corrupted buoys (4,17) were removed. Drift 14 and 15 are the same. These three major datasets were joined together based on a common buoy number and time field. Environmetal and oceanographic variables thought to be predictors of BW/SW habitat were extracted from NOAA's Environmental Research Division Data Access Program (ERDDAP) and Hybrid Coordinate Ocean Model (HYCOM) using matchEnvData function in package PAMmisc. Variables at depth were calculated using function from Taiki and formula from McCullough et al 2021. Distance to slope and bathymetric slope were calculated from a bathymetry TIF taken from GEBCO. Can show table of variables and justification by papers (Virgili et al. 2022).

@@

@@

\[Add here.\] \[Weekly/daily plot of acoustic presence of whales and ships over time from each drift? See Trickey et al. 2022\]

>>>>

Drifter tracks were rounded to nearest 20 minutes, lost buoys (1,2,3,5,6,9,11) and corrupted buoys (4,17) were removed. Drift 14 and 15 are the same. These three major datasets were joined together based on a common buoy number and time field.

\[Environmental Data\]\
Environmetal and oceanographic variables thought to be predictors of BW/SW habitat were extracted from NOAA's Environmental Research Division Data Access Program (ERDDAP) and Hybrid Coordinate Ocean Model (HYCOM) using matchEnvData function in package PAMmisc. Variables at depth were calculated using function from Taiki and formula from McCullough et al 2021. Distance to slope and bathymetric slope were calculated from a bathymetry TIF taken from GEBCO. Can show table of variables and justification by papers (Virgili et al. 2022).

[On wind curl stress]{.underline}: "Positive wind stress curl lifts the thermocline, which results in enhanced primary production" (Manocci et al 2015).

@@

[Example of GAM]{.underline}: Manocci et al. 2015.

@@

\[Weekly/daily plot of acoustic presence of whales and ships over time from each drift? See JS Trickey et al. 2022, Fig 3\]
